ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-06 paper.tex
it takes a long paper...

\documentclass[a4paper, 10pt, american, titlepage]{article}

% useful packages
\usepackage[utf8]{inputenc} % UTF-8 support
\usepackage{minted} % for code snippets
\usepackage[american]{babel} % for changing particular titles
\usepackage{csquotes} % recommended for biblatex
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol
\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables
\usepackage{CJKutf8} % for Japanese UTF-8 characters

@@

@@

	\vfill

@@

\vfill

\clearpage

% more breathing room
\setstretch{1.5}

\begin{abstract}
Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
tourist attractions. Most people who visit the site do not have the opportunity
to experience the rich art and culture that are part of its history. We worked
with our sponsor, Kyoto VR, to create an app that would allow visitors of
Kinkaku-ji to better experience these aspects of the site. We used Unity to
create an audio tour app that provides historical insight on the location,
displays galleries of art throughout the visit, and offers accessibility
features through AR. We also developed a tool to aid in the design and creation
of audio tours. We hope our app will enhance the experience of visiting
Kinkaku-ji.  
\end{abstract}

@@

\clearpage

@@

\clearpage

% now comes the table of contents, list of figures, and list of tables
% these should be single spaced
\begin{singlespace}
	\tableofcontents
	% uncomment this if you want the Table of Contents to have an entry in the
	% table of contents
	% \addcontentsline{toc}{section}{Table of Contents}
	\clearpage

	\listoffigures
	% \addcontentsline{toc}{section}{List of Figures}
	\clearpage

	\listoftables
	% \addcontentsline{toc}{section}{List of Tables}
	\clearpage
\end{singlespace}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-example.jpg}
	% Note: you don't actually need the part in square brackets for the
	% caption, but if you omit it the regular caption text will be used for
	% the List of Figures entry.
	\caption[A virtual model of the solar system projected onto the real world
	using AR]{A virtual model of the solar system projected onto the real world
		using augmented reality~\autocite{tedx2016}}
	\label{fig:arExample}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-1.jpg}
	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
	\label{fig:kinkakuji1}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{ar-marker.jpg}
	\caption[Augmented reality markers]{Augmented reality
		markers~\autocite{jeriaska2010}}
	\label{fig:arMarker}
\end{figure}

\clearpage

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
	\caption[A screenshot from the AR game \textit{Pokémon Go}]{A screenshot
		from the AR game \textit{Pokémon Go}~\autocite{vastateparks2016}.}
	\label{fig:pokemonGo}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{izi-travel.png}
	\caption{A screenshot of the izi.TRAVEL app interface}
	\label{fig:iziTravel}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji.jpg}
	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
	\label{fig:kinkakuji}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-grounds.jpg}
    \caption[Expertly landscaped islands in the Kinkaku-ji mirror pond]{Expertly
		landscaped islands in the Kinkaku-ji mirror pond~\autocite{desousa2014}}
	\label{fig:kinkakujiGrounds}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{updated-editour.png}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
    \caption{The ``Welcome to Editour'' card providing basic instructions to
    get started}
	\label{fig:welcomeCard}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
	\caption{Editour when a region is being drawn, including the two dotted
		preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{rename-subcard-editour.png}
	\caption{The ``Rename'' subcard}
	\label{fig:renameSubcard}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{media-subcard-editour.png}
	\caption{The ``Media'' subcard}
	\label{fig:mediaSubcard}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Points'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
    \caption{The ``Delete'' subcard}
	\label{fig:deleteSubcard}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
    \caption{The upload subcard with an upload status}
	\label{fig:uploadingMessage}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
    \caption{The download card}
	\label{fig:downloadCard}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
    \caption{The jump card}
	\label{fig:jumpCard}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{super-famicom-controller.jpg}
    \caption[A Japanese Super Famicom controller.]{The inspiration for the
    colorscheme: a Japanese Super Famicom controller~\autocite{amos2017}.}
    \label{fig:superFamicomController}
\end{figure}

@@

% TODO make it so these images don't appear so far away (thank you LaTeX)
\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-instant.jpg}
	\caption{Google Translate camera feature in ``instant'' mode.}
	\label{fig:translateInstant}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-scan.jpg}
	\caption{Google Translate camera feature in ``scan'' mode}
	\label{fig:translateScan}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.8\textwidth]{translate-final-card.png}
	\caption{The final page seen after using ``scan'' mode in Google Translate}
	\label{fig:translateFinalCard}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.8\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{kinkakuji-ticket.jpeg}
    \caption{Kinkaku-ji ticket}
    \label{fig:kinkakujiTicket}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{souvenir.png}
	\caption{ARuko's virtual souvenir feature}
	\label{fig:souvenir}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{kinkakuji-horizontal.png}
	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
	\label{fig:kinkakujiHorizontal}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{old-ui.png}
	\caption{A screenshot of our early UI}
	\label{fig:oldUI}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{floating-cube.png}
	\caption{An ``art cube'' floating over the water containing a placeholder
    programming meme}
	\label{fig:floatingCube}
\end{figure}

@@

% TODO split up this figure into four separate figures, change references to
% refer to the correct ones
\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{adobe-xd-design.png}
	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
    {A screenshot of the Adobe XD project designed by Atticus Sims}
	\label{fig:adobeXdDesign}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption{Additions to Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{chapters-zoomed.png}
    \caption{Larger screenshot of the chapter selection screen mock-up}
    \label{fig:chaptersZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{gallery-zoomed.png}
    \caption{Larger screenshot of the transcript and image gallery mock-up}
    \label{fig:galleryZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{info-zoomed.png}
    \caption{Larger screenshot of the info button mock-up}
    \label{fig:infoZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{map-zoomed.png}
    \caption{Larger screenshot of the route screen mock-up}
    \label{fig:mapZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.6\textwidth]{translation-zoomed.png}
    \caption{Larger screenshot of the translation window mock-up}
    \label{fig:translationZoomed}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{issues-page-example.png}
	\caption{The GitHub issues tab for Editour}
	\label{fig:issuesPageExample}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{intersections-diagram.png}
	\caption{A visualization of the algorithm}
	\label{fig:intersectionsDiagram}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{ritsu-tour.png}
	\caption{The Ritsumeikan example tour used for testing}
	\label{fig:ritsuTour}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkaku-ji tour]{The original version
		of the Kinkaku-ji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
		version of the Kinkaku-ji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
	\caption{Tracking four image targets at once with improved info buttons.}
	\label{fig:fourIButtons}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{galaxy-s10+.jpg}
	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
		cameras~\autocite{yoo2019}}
	\label{fig:galaxyS10Plus}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{iphone-x.jpg}
	\caption[An iPhone X with a large notch]{An iPhone X with a large
		notch~\autocite{yoo2017}}
	\label{fig:iPhoneX}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}

@@

\clearpage

% references should be single spaced
\begin{singlespace}
	\printbibliography
	\addcontentsline{toc}{section}{References}
\end{singlespace}

\clearpage

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kanban-board.png}
	\caption{A screenshot of the Kanban board we used for developing our
    biweekly blog}
	\label{fig:kanbanBoard}
\end{figure}

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.8\textwidth]{reference-model.png}
    \caption{The reference model we used to implement the simulation}
    \label{fig:referenceModel}
\end{figure}

@@

\begin{figure}[h] \centering
    \includegraphics[width=\textwidth]{interactive-model.png}
    \caption{A diagram representing the physical model of the heart}
    \label{fig:interactiveModel}
\end{figure}

@@

\begin{figure}[h] \centering
    \includegraphics[width=\textwidth]{heart-gui.png}
    \caption{The GUI to enable five preprogrammed scenarios}
    \label{fig:heartGui}
\end{figure}

@@

\begin{table}[h]
\begin{singlespace}
\renewcommand{\arraystretch}{2.0} % add space between rows
\footnotesize % make font smaller
\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
	I enjoyed the audio tour & The image gallery added to the audio tour & I
	found the AR translation feature helpful & I found the AR map overlay
	helpful & The AR features were easy to use & Do you have any other thoughts
	on how to improve the experience? \\
	\hline

@@

	Agree & Agree & Strongly agree & Disagree & Neutral & Zoom in ar mode \\
\end{tabulary}
\end{singlespace}
\caption{Results of final field test survey}
\label{tab:testingSurveyResults}
\end{table}

\clearpage

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\textwidth]{no-ar-working.jpg}
	\caption{Noh artist dancing on the ground plane of the scene}
	\label{fig:noArWorking}
\end{figure}

>>>>

\documentclass[8pt, american, titlepage]{article}

% useful packages
\usepackage[utf8]{inputenc} % UTF-8 support
\usepackage{minted} % for code snippets
\usepackage[american]{babel} % for changing particular titles
\usepackage{csquotes} % recommended for biblatex
\usepackage{graphicx} % for images
\usepackage[gen]{eurosym} % for literally just the euro symbol
\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables
\usepackage{CJKutf8} % for Japanese UTF-8 characters
\usepackage{morefloats}

@@

\geometry{paperwidth=340mm, paperheight=16383pt, marginparsep=20pt, marginparwidth=100pt, textheight=16263pt, footskip=40pt}

\setcounter{totalnumber}{100}

@@

	%\vfill

@@

%\vfill

%\clearpage

%\begin{abstract}
\section*{Abstract}

Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
tourist attractions. Most people who visit the site do not have the opportunity
to experience the rich art and culture that are part of its history. We worked
with our sponsor, Kyoto VR, to create an app that would allow visitors of
Kinkaku-ji to better experience these aspects of the site. We used Unity to
create an audio tour app that provides historical insight on the location,
displays galleries of art throughout the visit, and offers accessibility
features through AR. We also developed a tool to aid in the design and creation
of audio tours. We hope our app will enhance the experience of visiting
Kinkaku-ji.  
%\end{abstract}

@@

%\clearpage

@@

%\clearpage

% now comes the table of contents, list of figures, and list of tables
\tableofcontents
% uncomment this if you want the Table of Contents to have an entry in the
% table of contents
% \addcontentsline{toc}{section}{Table of Contents}
%\clearpage

\listoffigures
% \addcontentsline{toc}{section}{List of Figures}
%\clearpage

\listoftables
% \addcontentsline{toc}{section}{List of Tables}
%\clearpage

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{ar-example.jpg}
	% Note: you don't actually need the part in square brackets for the
	% caption, but if you omit it the regular caption text will be used for
	% the List of Figures entry.
	\caption[A virtual model of the solar system projected onto the real world
	using AR]{A virtual model of the solar system projected onto the real world
		using augmented reality~\autocite{tedx2016}}
	\label{fig:arExample}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji-1.jpg}
	\caption[The Golden Pavilion]{The Golden Pavilion~\autocite{fan2018}}
	\label{fig:kinkakuji1}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{ar-marker.jpg}
	\caption[Augmented reality markers]{Augmented reality
		markers~\autocite{jeriaska2010}}
	\label{fig:arMarker}
\end{figure}

%\clearpage

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{pokemon-go.jpg}
	\caption[A screenshot from the AR game \textit{Pokémon Go}]{A screenshot
		from the AR game \textit{Pokémon Go}~\autocite{vastateparks2016}.}
	\label{fig:pokemonGo}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{izi-travel.png}
	\caption{A screenshot of the izi.TRAVEL app interface}
	\label{fig:iziTravel}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji.jpg}
	\caption[The Golden Pavilion of Kinkaku-ji, Kyoto, Japan]{The Golden
		Pavilion of Kinkaku-ji, Kyoto, Japan~\autocite{davidson2005}}
	\label{fig:kinkakuji}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji-grounds.jpg}
    \caption[Expertly landscaped islands in the Kinkaku-ji mirror pond]{Expertly
		landscaped islands in the Kinkaku-ji mirror pond~\autocite{desousa2014}}
	\label{fig:kinkakujiGrounds}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{updated-editour.png}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{welcome-card-editour.png}
    \caption{The ``Welcome to Editour'' card providing basic instructions to
    get started}
	\label{fig:welcomeCard}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{drawing-region-editour.png}
	\caption{Editour when a region is being drawn, including the two dotted
		preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{rename-subcard-editour.png}
	\caption{The ``Rename'' subcard}
	\label{fig:renameSubcard}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{media-subcard-editour.png}
	\caption{The ``Media'' subcard}
	\label{fig:mediaSubcard}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Points'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{delete-subcard-editour.png}
    \caption{The ``Delete'' subcard}
	\label{fig:deleteSubcard}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{uploading-message-editour.png}
    \caption{The upload subcard with an upload status}
	\label{fig:uploadingMessage}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{download-card-editour.png}
    \caption{The download card}
	\label{fig:downloadCard}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{jump-card-editour.png}
    \caption{The jump card}
	\label{fig:jumpCard}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{super-famicom-controller.jpg}
    \caption[A Japanese Super Famicom controller.]{The inspiration for the
    colorscheme: a Japanese Super Famicom controller~\autocite{amos2017}.}
    \label{fig:superFamicomController}
\end{figure}

@@

% TODO make it so these images don't appear so far away (thank you LaTeX)
\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{translate-instant.jpg}
	\caption{Google Translate camera feature in ``instant'' mode.}
	\label{fig:translateInstant}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{translate-scan.jpg}
	\caption{Google Translate camera feature in ``scan'' mode}
	\label{fig:translateScan}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{translate-final-card.png}
	\caption{The final page seen after using ``scan'' mode in Google Translate}
	\label{fig:translateFinalCard}
\end{figure}

@@

\begin{figure}[p]
	\centering
    \includegraphics[width=0.2\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{kinkakuji-ticket.jpeg}
    \caption{Kinkaku-ji ticket}
    \label{fig:kinkakujiTicket}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{souvenir.png}
	\caption{ARuko's virtual souvenir feature}
	\label{fig:souvenir}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji-horizontal.png}
	\caption{Untextured Golden Pavilion model sitting horizontally on ticket}
	\label{fig:kinkakujiHorizontal}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{old-ui.png}
	\caption{A screenshot of our early UI}
	\label{fig:oldUI}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{floating-cube.png}
	\caption{An ``art cube'' floating over the water containing a placeholder
    programming meme}
	\label{fig:floatingCube}
\end{figure}

@@

% TODO split up this figure into four separate figures, change references to
% refer to the correct ones
\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{adobe-xd-design.png}
	\caption[A screenshot of the Adobe XD project designed by Atticus Sims]
    {A screenshot of the Adobe XD project designed by Atticus Sims}
	\label{fig:adobeXdDesign}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{editour-additions.png}
	\caption{Additions to Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{chapters-zoomed.png}
    \caption{Larger screenshot of the chapter selection screen mock-up}
    \label{fig:chaptersZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{gallery-zoomed.png}
    \caption{Larger screenshot of the transcript and image gallery mock-up}
    \label{fig:galleryZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{info-zoomed.png}
    \caption{Larger screenshot of the info button mock-up}
    \label{fig:infoZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{map-zoomed.png}
    \caption{Larger screenshot of the route screen mock-up}
    \label{fig:mapZoomed}
\end{figure}

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{translation-zoomed.png}
    \caption{Larger screenshot of the translation window mock-up}
    \label{fig:translationZoomed}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{issues-page-example.png}
	\caption{The GitHub issues tab for Editour}
	\label{fig:issuesPageExample}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{intersections-diagram.png}
	\caption{A visualization of the algorithm}
	\label{fig:intersectionsDiagram}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{ritsu-tour.png}
	\caption{The Ritsumeikan example tour used for testing}
	\label{fig:ritsuTour}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkaku-ji tour]{The original version
		of the Kinkaku-ji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
		version of the Kinkaku-ji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{four-i-buttons.png}
	\caption{Tracking four image targets at once with improved info buttons.}
	\label{fig:fourIButtons}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{galaxy-s10+.jpg}
	\caption[A Samsung Galaxy S10+ phone with distinctive ``hole punch''
	cameras]{A Samsung Galaxy S10+ phone with distinctive ``hole punch''
		cameras~\autocite{yoo2019}}
	\label{fig:galaxyS10Plus}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{iphone-x.jpg}
	\caption[An iPhone X with a large notch]{An iPhone X with a large
		notch~\autocite{yoo2017}}
	\label{fig:iPhoneX}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}

@@

%\clearpage

\printbibliography
\addcontentsline{toc}{section}{References}

%\clearpage

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{kanban-board.png}
	\caption{A screenshot of the Kanban board we used for developing our
    biweekly blog}
	\label{fig:kanbanBoard}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{reference-model.png}
    \caption{The reference model we used to implement the simulation}
    \label{fig:referenceModel}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{interactive-model.png}
    \caption{A diagram representing the physical model of the heart}
    \label{fig:interactiveModel}
\end{figure}

@@

\begin{figure}[p] \centering
    \includegraphics[width=0.2\textwidth]{heart-gui.png}
    \caption{The GUI to enable five preprogrammed scenarios}
    \label{fig:heartGui}
\end{figure}

@@

\begin{table}[h]
\renewcommand{\arraystretch}{2.0} % add space between rows
\footnotesize % make font smaller
\begin{tabulary}{\textwidth}{ L | L | L | L | L | L }
	I enjoyed the audio tour & The image gallery added to the audio tour & I
	found the AR translation feature helpful & I found the AR map overlay
	helpful & The AR features were easy to use & Do you have any other thoughts
	on how to improve the experience? \\
	\hline

@@

	Agree & Agree & Strongly agree & Disagree & Neutral & Zoom in ar mode \\
\end{tabulary}
\caption{Results of final field test survey}
\label{tab:testingSurveyResults}
\end{table}

%\clearpage

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=0.2\textwidth]{no-ar-working.jpg}
	\caption{Noh artist dancing on the ground plane of the scene}
	\label{fig:noArWorking}
\end{figure}
